---
title: "Data Inspection for Final Project"
output: github_document
date: '2022-04-20'
---
First, I will load in the packages (tidyverse, lemon, knitr). This code is in the script but not knit to the markdown document for readability. 
```{r,setup, include=FALSE}
library(tidyverse)
library(lemon)
library(knitr)
```

I also read in the "DS-KROK4BDJ.txt" file, which is a tsv downloaded from our paper of choice and (I believe) contains all the data we will need to work with, including sample IDs, geographic information, and sequences. 
```{r,my-chunk, echo=FALSE}
bdj<-read_tsv("DS-KROK4BDJ.txt", show_col_types = FALSE )
column_names <- colnames(bdj)
```
After reading in the file, I inspect the column dimensions
```{r}
dim(bdj)
```

There are 80 columns and 124 rows in this file. Next check out column names. 
```{r}
print(column_names)
```
Let's look at the first 5 rows in this file. It's a large chunk, but very interesting. Scroll side to side to see the whole chunk. 
```{r}
kable(bdj[1:5, ])
```
