---
title: "Data Inspection for Final Project"
output: github_document
date: '2022-04-20'
---
First, I will load in the packages (tidyverse, lemon, knitr). This code is in the script but not knit to the markdown document for readability. 
```{r,setup, include=FALSE}
library(tidyverse)
library(lemon)
library(knitr)
```

I also read in the "DS-KROK4BDJ.txt" file, which is a tsv downloaded from our paper of choice and (I believe) contains all the data we will need to work with, including sample IDs, geographic information, and sequences. 
```{r,my-chunk, echo=FALSE}
bdj<-read_tsv("DS-KROK4BDJ.txt", show_col_types = FALSE )
column_names <- colnames(bdj)
```
After reading in the file, I inspect the column dimensions
```{r}
dim(bdj)
```

There are 80 columns and 124 rows in this file. Next check out column names. 
```{r}
print(column_names)
```
Let's look at the first 5 rows in this file. It's a large chunk, but very interesting. Scroll side to side to see the whole chunk. 
```{r}
kable(bdj[1:5, ])
```
From this point, we can pick out columns that we want to work with. For practice, I will select the phylum-subspecies taxID and name columns (14 columns total) and convert them to factor. After this (hidden) code chunk, the "bdj" object (our data) columns with these names will be converted from "numeric" or "character" to "factor". Since they are now factors, we can run other analyses on them and visualize how many of each, etc. 

```{r, chunk, echo=FALSE, include=FALSE}

bdj$phylum_taxID = as.factor(as.numeric(bdj$phylum_taxID))
bdj$class_taxID = as.factor(as.numeric(bdj$class_taxID))
bdj$order_taxID = as.factor(as.numeric(bdj$order_taxID))
bdj$family_taxID = as.factor(as.numeric(bdj$family_taxID))
bdj$genus_taxID = as.factor(as.numeric(bdj$genus_taxID))
bdj$species_taxID = as.factor(as.numeric(bdj$species_taxID))
bdj$subspecies_taxID = as.factor(as.numeric(bdj$subspecies_taxID))

bdj$phylum_name = as.factor(as.numeric(bdj$phylum_name))
bdj$class_name = as.factor(as.numeric(bdj$class_name))
bdj$order_name = as.factor(as.numeric(bdj$order_name))
bdj$family_name = as.factor(as.numeric(bdj$family_name))
bdj$genus_name = as.factor(as.numeric(bdj$genus_name))
bdj$species_name = as.factor(as.numeric(bdj$species_name))
bdj$subspecies_name = as.factor(as.numeric(bdj$subspecies_name))
```
(The code is here, trust me. Check the Rmd file if you want to see it)
